Classless Java: Tuning Java Interfaces

### 2015-11-25 paper/sections/CaseStudy.tex
Game example
fix bibtex errors

The \emph{Expression Problem} (EP)~\cite{wadler98expression-problem}
is a well-known problem about modular extensibility issues in software
evolution. Recently, a new solution~\cite{eptrivially} that uses only
covariant type refinement that has been shown to work in Java. When
that solution is modelled with interfaces and default methods, it can
even provide independent extensibility: that is, the ability to
assemble a system, from multiple, independently developed extensions.
Unfortunatelly, a plain Java solution has alot of code verbosity in
Java due to code required for instantiation, which makes the solution 
cumbersome to use. The \mixin annotation helps to remove such code, and 
makes the solution quite easy to use.
\bruno{We should try to do some space saving in here. You could, for example 
combine the code for the initial system with the code for a new operation in a figure/table 
with 2 colums. Then just refer to the Table/Figure in the text.}

@@

\paragraph{Independent Extensibility}
To show that our approach supports independent extensibility~\cite{odersky}, we first define a
new operation \texttt{collectLit} (which collects all
literal components in an expression) on expressions. For space reasons, 
we omit the definitions of the methods: 
\bruno{No need to show full code in the paper. You can just put \ldots in the body of the collectLit methods.}

@@

\noindent The \mixin annotation allowed us to reduce the interfaces/classes used
in Bono et al.'s implementation by 21.4\% (from 14 to 11). The
reductions was due to the replacement of instantiation classes with
generated \texttt{of} methods. The number of source lines of code (SLOC)
was reduced by 40\%\bruno{explain why? we generate code for getters/setters?}. 
To ensure a fair comparison, we used the same coding style as Bono's.

>>>>

The \emph{Expression Problem} (EP)~\cite{wadler98expression}
is a well-known problem about modular extensibility issues in software
evolution. Recently, a new solution~\cite{eptrivially} that uses only
covariant type refinement that has been shown to work in Java. When
that solution is modelled with interfaces and default methods, it can
even provide independent extensibility: that is, the ability to
assemble a system, from multiple, independently developed extensions.
Unfortunatelly, a plain Java solution has alot of code verbosity in
Java due to code required for instantiation, which makes the solution 
cumbersome to use. The \mixin annotation helps to remove such code, and 
makes the solution quite easy to use.
\bruno{We should try to do some space saving in here. You could, for example 
combine the code for the initial system with the code for a new operation in a figure/table 
with 2 colums. Then just refer to the Table/Figure in the text.}

@@

\paragraph{Independent Extensibility}
To show that our approach supports independent extensibility~\cite{zenger05independentlyextensible}, we first define a
new operation \texttt{collectLit} (which collects all
literal components in an expression) on expressions. For space reasons, 
we omit the definitions of the methods: 
\bruno{No need to show full code in the paper. You can just put \ldots in the body of the collectLit methods.}

@@

\noindent The \mixin annotation allowed us to reduce the interfaces/classes used
in Bono et al.'s implementation by 21.4\% (from 14 to 11). The
reductions was due to the replacement of instantiation classes with
generated \texttt{of} methods. The number of source lines of code (SLOC)
was reduced by 40\%\bruno{explain why? we generate code for getters/setters?}. 
To ensure a fair comparison, we used the same coding style as Bono et al.'s.
